### 2016-11-18 README.Rmd
Update README

@@

For each dataset, you can see the helpfiles for the data for more information. For example:

@@

There are several functions in this package that help to take the data on rainfall and storm tracks stored in the package and use them, in conjunction with thresholds for the distance to the storm tracks and the amount of rainfall required for exposure, to create time series of exposure that can be easily integrated into time series datasets of, for example, health data.

@@

For example, to get a dataset of all the storms to which Orleans Parish (FIPS 22071), and Newport News, Virginia (FIPS 51700), were exposed between 1995 and 2005, where "exposed" means that the storm passed within 100 kilometers of the county center and the rainfall over three days was 100 millimeters or more, you could run:

@@

In addition to giving you the names and closest dates of each storm for each county (`closest_date`-- note, this is given using the UTC timezone), this function also gives you the distance between the county and the storm's track at the time when the storm was closest to the county's population weighted center (`storm_dist`, in kilometers) and the total precipitation over the included days (`tot_precip`).

To get a dataframe listing the relevant storms for multi-county communities, you can use the `multi_county_rain` function in a similar way:

```{r warning = FALSE}
communities <- data.frame(commun = c(rep("ny", 6), "no", "new"),
                         fips = c("36005", "36047", "36061",
                                  "36085", "36081", "36119",
                                  "22071", "51700"))
rain_storm_df <- multi_county_rain(communities = communities,
                                   start_year = 1995, end_year = 2005,
                                   rain_limit = 100, dist_limit = 100,
                                   days_included = c(-1, 0, 1))
```

This output includes columns for the average closest distance for any of the counties in the community (`mean_dist`), the average precipitation for all the counties (`mean_precip`), the highest precipitation for any of the counties (`max_rain`), and the smallest distance between the storm track and any of the county population-weighted centers (`min_dist`).

>>>>

## Overview

This package is meant to add users in creating datasets of tropical storm exposure at the county level for US counties. It covers counties in the eastern half of the United States and includes all Atlantic basin tropical storms between 1988 and 2015 (although data for some hazards are only available for some of those years). Tropical storm exposure datasets can be generated based on distance to storm tracks, rain, wind, or NOAA storm event listings (including tornado and flood events).

For non-R users, we are developing [a web application](https://zhimingguo.shinyapps.io/Hurricane_Map1/) to allow similar functionality. The exposure datasets generated by this web application can be downloaded as flat files and read into other software.

@@

For each dataset, you can see the helpfiles for the data for more information by using the `?` call with the dataset name. For example, to access the documentation for the `hurr_tracks` dataset, you can run:

@@

There are several functions in this package that help to take the data on rainfall, wind, storm events, and storm tracks stored in the package and use them, in conjunction with user-specified thresholds, to create county-level time series of exposure that can be easily integrated into time series datasets of, for example, health data.

@@

For example, to get a dataset of all the storms to which Orleans Parish (FIPS 22071), and Newport News, Virginia (FIPS 51700), were exposed between 1995 and 2005, where "exposed" means that the storm passed within 100 kilometers of the county center and the rainfall over three days was 100 millimeters or more, you can run:

@@

In addition to giving you the names and closest dates of each storm for each county (`closest_date`-- note, this is given based on local time), this function also gives you the distance between the county and the storm's track at the time when the storm was closest to the county's population weighted center (`storm_dist`, in kilometers) and the total precipitation over the included days (`tot_precip`). The returned dataframe also includes columns with the local time (based on the counties timezone using the [`countytimezones`](https://cran.r-project.org/web/packages/countytimezones/index.html) R package) when the storm was closest to that county and the time in UTC (to aid in pairing with other weather data in UTC).

Some health data is aggregated at the multi-county, rather than county, level (e.g., data is available for New York City as a whole, rather than for each county in the city). To get a dataframe listing the relevant storms for multi-county communities, you can use the `multi_county_rain` function in a similar way, passing in a `communities` dataframe that lists all counties associated with each community:

```{r warning = FALSE}
communities <- data.frame(commun = c(rep("ny", 6), "no", "new"),
                         fips = c("36005", "36047", "36061",
                                  "36085", "36081", "36119",
                                  "22071", "51700"))
multi_county_rain(communities = communities,
                  start_year = 1995, end_year = 2005,
                  rain_limit = 100, dist_limit = 100,
                  days_included = c(-1, 0, 1))
```

This output includes columns for the average closest distance, averaged across all counties in the community (`mean_dist`), the average precipitation for all community counties (`mean_precip`), the highest precipitation for any community county (`max_rain`), and the smallest distance between the storm track and any of the county population-weighted centers (`min_dist`).

Similarly, `county_wind` and `multi_county_wind` functions can be used to generate exposure datasets based on wind exposure during tropical storms. For example, to determine all storms with sustained winds of 20 m / s or more for Orleans Parish (FIPS 22071), and Newport News, Virginia (FIPS 51700) between 1995 and 2005, you can run:

```{r}
county_wind(counties = c("22071", "51700"),
            start_year = 1995, end_year = 2005,
            wind_limit = 20)
```

This function returns a dataframe that lists all the storms to which each county was exposed. The `vmax_sust` column gives the highest sustained wind modeled at the county's population mean center, while the `vmax_gust` gives the highest gust wind speed modeled there.
